---
title: "Sustainable Development Goals Exploratory Data Analysis"
author: "Eric Scheier"
date: "2/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(foreign)
```

# Getting The Data

Data is available from github [here](https://github.com/sdsna/2019USCitiesIndex):

Here were some initial variables I defined while trying to get the data.
```{r}
github_url <- "https://github.com/sdsna/2019USCitiesIndex"
github_url_dta <- "https://github.com/sdsna/2019USCitiesIndex/blob/master/2019USCitiesIndexResults.dta"
github_url_xlsx <- "https://github.com/sdsna/2019USCitiesIndex/blob/master/2019USCitiesIndexResults.xlsx?raw=true"
```

Directions for data acquisition:

0. If the data is in your working directory, proceed to the next code block.
1. Download the data manually from [here](https://github.com/sdsna/2019USCitiesIndex/blob/master/2019USCitiesIndexResults.xlsx?raw=true).
2. Download the `Results` and `Codebook` sheets as `.csv` files.

Now we have our data in `.csv` format and we want to join it all together nicely.

```{r}
library(tidyverse)
codebook <- read_csv("2019USCitiesIndexResults - Codebook.csv")
results <- read_csv("2019USCitiesIndexResults - Results.csv")
populations <- read_csv("cbsa-est2018-alldata.csv")

names(codebook)
names(results)
names(populations)
```

# Data Munging

We have 5 types of variables in the `results` dataset:

1. Descriptive
2. Normalized
3. Raw Data
4. Scores
5. Ranks

```{r}
results[c(1:5,
          (nrow(results)-5):nrow(results)),
        c("rank_sdgIndex", 
       "msa", 
       "score_sdgi", 
       paste0(rep("score_sdg",17),c(1:13,15:16)))]
```


```{r}

scores <- runif(n = 17,min=0,max=100) #rep(100,17)
sdg_scores <- data.frame(sdg=1:17, score=scores)



pie <- ggplot(sdg_scores, aes(x=sdg, y=score, fill=factor(sdg))) + 
  geom_col(width = 1) + 
  #ylim(c(-50, 100)) + 
  coord_polar(theta = "x", direction=1) + 
  scale_fill_manual(values=c("#e5243b", 
                             "#DDA63A", 
                             "#4C9F38",
                             "#C5192D",
                             "#FF3A21",
                             "#26BDE2",
                             "#FCC30B",
                             "#A21942",
                             "#FD6925",
                             "#DD1367",
                             "#FD9D24",
                             "#BF8B2E",
                             "#3F7E44",
                             "#0A97D9",
                             "#56C02B",
                             "#00689D",
                             "#19486A"
                             ))

pie
```

```{r}
sdg_scores_all <- 
```


# Questions
## Rubric Questions

1. What is the objective of the visualisations?
What elements of the design are related to that objective?
Are those elements effective in achieving the objective
Why or why not?
Are the collection of visualisations necessary and sufficient evidence for the story, i.e. are they complementary/reinforcing?
How might you approach this task yourself?


## Our Questions

# 1. What visualizations are used?

2. How restrictive is framework?

3. Do the colors have meaning?

4. What are some options for other visualizations?

